---
title: "Cut and Tag QC"
author: "Steven Yu"
date: "2025-07-01"
output: workflowr::wflow_html
editor_options:
  chunk_output_type: inline
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
	echo = TRUE,
	message = FALSE,
	warning = FALSE,
	dev = c("png","pdf")
)
```

## Cut And Tag QC

#### Loading Packages 
```{r load packages}
library(tidyverse)
library(readr)
library(edgeR)
library(ComplexHeatmap)
library(data.table)
library(dplyr)
library(stringr)
library(ggplot2)
library(viridis)
library(DT)
library(kableExtra)
library(genomation)
library(GenomicRanges)
library(chromVAR) ## For FRiP analysis and differential analysis
library(DESeq2) ## For differential analysis section
library(ggpubr) ## For customizing figures
library(corrplot) ## For correlation plot
library(ggpmisc)
library(gcplyr)
```

#### Data Initialization
```{r init}
sampleinfo <- read_delim("data/sample_info.tsv", delim = "\t")
multiqc_gene_stats_trim <- read_delim("data/multiqc_data_trim/multiqc_general_stats.txt",delim = "\t")
multiqc_fastqc_trim <- read_delim("data/multiqc_data_trim/multiqc_fastqc.txt",delim = "\t")
```

#### Functions
```{r functions}
drug_pal <- c("#8B006D","#DF707E","#F1B72B", "#3386DD","#707031","#41B333")
pca_plot <-
  function(df,
           col_var = NULL,
           shape_var = NULL,
           title = "") {
    ggplot(df) + geom_point(aes_string(
      x = "PC1",
      y = "PC2",
      color = col_var,
      shape = shape_var
    ),
    size = 5) +
      labs(title = title, x = "PC 1", y = "PC 2") +
      scale_color_manual(values = c(
        "#8B006D",
        "#DF707E",
        "#F1B72B",
        "#3386DD",
        "#707031",
        "#41B333"
      ))
  }
pca_var_plot <- function(pca) {
  # x: class == prcomp
  pca.var <- pca$sdev ^ 2
  pca.prop <- pca.var / sum(pca.var)
  var.plot <-
    qplot(PC, prop, data = data.frame(PC = 1:length(pca.prop),
                                      prop = pca.prop)) +
    labs(title = 'Variance contributed by each PC',
         x = 'PC', y = 'Proportion of variance')
  plot(var.plot)
}

calc_pca <- function(x) {
  # Performs principal components analysis with prcomp
  # x: a sample-by-gene numeric matrix
  prcomp(x, scale. = TRUE, retx = TRUE)
}

get_regr_pval <- function(mod) {
  # Returns the p-value for the Fstatistic of a linear model
  # mod: class lm
  stopifnot(class(mod) == "lm")
  fstat <- summary(mod)$fstatistic
  pval <- 1 - pf(fstat[1], fstat[2], fstat[3])
  return(pval)
}

plot_versus_pc <- function(df, pc_num, fac) {
  # df: data.frame
  # pc_num: numeric, specific PC for plotting
  # fac: column name of df for plotting against PC
  pc_char <- paste0("PC", pc_num)
  # Calculate F-statistic p-value for linear model
  pval <- get_regr_pval(lm(df[, pc_char] ~ df[, fac]))
  if (is.numeric(df[, f])) {
    ggplot(df, aes_string(x = f, y = pc_char)) + geom_point() +
      geom_smooth(method = "lm") + labs(title = sprintf("p-val: %.2f", pval))
  } else {
    ggplot(df, aes_string(x = f, y = pc_char)) + geom_boxplot() +
      labs(title = sprintf("p-val: %.2f", pval))
  }
}
x_axis_labels = function(labels, every_nth = 1, ...) {
  axis(side = 1,
       at = seq_along(labels),
       labels = F)
  text(
    x = (seq_along(labels))[seq_len(every_nth) == 1],
    y = par("usr")[3] - 0.075 * (par("usr")[4] - par("usr")[3]),
    labels = labels[seq_len(every_nth) == 1],
    xpd = TRUE,
    ...
  )
}
```

### Basic Stats

#### Data Processing
```{r Data Processig}
combo_trim_df <- multiqc_fastqc_trim %>% 
 extract(., Sample, into = c("prefix","read"), regex= "(.+)_R(\\d+)", remove=FALSE) %>% 
  mutate(read = paste0("R", read)) %>% 
  left_join(., sampleinfo, by =c("prefix"="Library ID")) %>% 
  left_join(., multiqc_gene_stats_trim, by = c("Sample" = "Sample")) %>% 
  mutate(ind=factor(Individual, levels = c("Ind1","Ind2","Ind3","Ind4","Ind5"))) %>% 
  mutate(trt=factor(Treatment, levels = c("VEH","5FU","DOX"))) %>% 
  mutate(time=factor(Timepoint, levels=c("24T","24R","144R")))
combo_trim_df <- combo_trim_df[(!combo_trim_df$trt %in% "5FU"),]
```

#### Data Visualization
```{r Data Visualization 1}
combo_trim_df %>% 
  dplyr::filter(read=="R1") %>% 
  group_by(trt, time, Histone_Mark) %>% 
  tally() %>% 
  ggplot(., aes(x = time, y= n))+
  geom_col(position="dodge",aes(fill=trt)) + 
  facet_wrap(~Histone_Mark)+
  theme(axis.text.x=element_text(angle=90))+
  ylab("number of samples")+
  ggtitle("Breakdown of samples by mark and trt-time")
```

```{r Data Visualization 2}
combo_trim_df %>% 
  dplyr::filter(read=="R1") %>% 
  group_by(trt,time,Histone_Mark) %>% 
  tally() %>% 
  pivot_wider(., id_cols=c(trt,time), names_from = Histone_Mark, values_from = n) %>% 
  kable(.,caption = ("Sample counts")) %>% 
  kable_paper("striped", full_width = FALSE) %>%
  kable_styling(full_width = FALSE,font_size = 16) %>%
  scroll_box(width = "100%", height = "500px")
```

### Visualization of Counts
```{r ct vis histo, fig.width = 14}
combo_trim_df %>% 
  dplyr::filter(read=="R1") %>% 
  ggplot(., aes(x = Sample, y= `Total Sequences`))+
  geom_col(aes(fill=Histone_Mark)) + 
  theme(axis.text.x=element_text(vjust = .2,angle=90))+
  ylab("sequene count")+
  ggtitle("Read counts by sample and histone mark trimmed adapters")+
  scale_y_continuous( expand = expansion(mult = c(0, .1)))
```

#### Tagging Questionable Libraries by Counts
```{r ct tag}
questionable_ct <- combo_trim_df %>%
  dplyr::filter(`Total Sequences` < 2e6) %>%
  dplyr::select(Sample, `Total Sequences`) %>% distinct()
questionable_ct
```

```{r ct vis box}
combo_trim_df %>% 
  dplyr::filter(read=="R1") %>% 
   ggplot(., aes(x = Histone_Mark, y= `Total Sequences`))+
geom_boxplot(aes(fill=Histone_Mark)) + 
    geom_point(aes(color=ind))+
  facet_wrap(trt~time)+
  ylab("count")+
  theme(axis.text.x=element_text(vjust = .2,angle=90))+
  ggtitle("Sequence count by trt and time trimmed adapter")
```

### Trim Info
```{r trim info 1}
combo_trim_df %>% 
  ggplot(., aes(x = read, y= avg_sequence_length))+
geom_boxplot(aes(fill=read))
```

```{r trim info 2}
combo_trim_df %>% 
  ggplot(., aes(x = read, y= avg_sequence_length))+
geom_boxplot(aes(fill=Histone_Mark)) +
  ggtitle("Boxplot of trim read length across histone marks")
```

```{r trim info 3}
combo_trim_df %>% 
  datatable(., options = list(scrollX = TRUE, 
                              scrollY = "400px",
                              scrollCollapse = TRUE,
                              fixedColumns = list(leftColumns =2),
                              fixedHeader= TRUE),
            extensions = c("FixedColumns","Scroller"),
            class = "display")
```

```{r trim info 4, fig.width = 14}
combo_trim_df %>% 
  dplyr::filter(read=="R1") %>% 
  ggplot(., aes(x = Sample, y= avg_sequence_length))+
geom_col(aes(fill=Histone_Mark)) +
  geom_hline( yintercept = 75)+
  theme_classic()+
  ggtitle("Graph of average read length across R1 samples")+ theme(axis.text.x=element_text(vjust = .2,angle=90))+
  scale_y_continuous( expand = expansion(mult = c(0, .1)))
```

```{r trim info 5, fig.width = 14}
combo_trim_df %>% 
  dplyr::filter(read=="R2") %>% 
  ggplot(., aes(x = Sample, y= avg_sequence_length))+
geom_col(aes(fill=Histone_Mark)) +
  geom_hline( yintercept = 75)+
  theme_classic()+
  ggtitle("Graph of average read length across R2 samples")+ theme(axis.text.x=element_text(vjust = .2,angle=90))+
  scale_y_continuous( expand = expansion(mult = c(0, .1)))
```

```{r trim info 6, fig.width = 14}
combo_trim_df %>% 
  dplyr::filter(read=="R1") %>% 
  ggplot(., aes(x = Sample, y= `%GC`))+
  geom_col(aes(fill=Histone_Mark)) +
  theme_classic()+
  ggtitle("Graph of %GC for R1 trimmed")+ 
  theme(axis.text.x=element_text(vjust = .2,angle=90))+
  scale_y_continuous( expand = expansion(mult = c(0, .1)))
```

```{r trim info 7, fig.width = 14}
combo_trim_df %>% 
  dplyr::filter(read=="R2") %>% 
  ggplot(., aes(x = Sample, y= `%GC`))+
  geom_col(aes(fill=Histone_Mark)) +
  theme_classic()+
  ggtitle("Graph of %GC for R2 trimmed")+ 
  theme(axis.text.x=element_text(vjust = .2,angle=90))+
  scale_y_continuous( expand = expansion(mult = c(0, .1)))
```

### Duplication Info
```{r dup info 1}
combo_trim_df %>% 
  dplyr::filter(read=="R1") %>% 
  ggplot(., aes(x = Histone_Mark, y= `FastQC_mqc-generalstats-fastqc-percent_duplicates`))+
  geom_boxplot(aes(fill=Histone_Mark)) + 
    geom_point(aes(color=ind))+
  facet_wrap(trt~time)+
  ylab("percent duplication")+
  theme(axis.text.x=element_text(angle=90))+
  ggtitle("Duplication percentage (R1 trimmed)")
```

```{r dup info 2}
combo_trim_df %>% 
  dplyr::filter(read=="R1") %>% 
  ggplot(., aes(x = interaction(time,trt), y= `FastQC_mqc-generalstats-fastqc-percent_duplicates`))+
  geom_boxplot(aes(fill=Histone_Mark)) + 
  geom_point(aes(color=ind))+
facet_wrap(~Histone_Mark)+
  ylab("percent duplication")+
  theme(axis.text.x=element_text(angle=90))+
  ggtitle("Duplication percentage (R1 trimmed)")
```

```{r dup info 3, fig.width = 14}
combo_trim_df %>% 
  dplyr::filter(read=="R1") %>% 
  ggplot(., aes(x = Sample, y= `FastQC_mqc-generalstats-fastqc-percent_duplicates`))+
  geom_col(aes(fill=Histone_Mark)) +
  theme_classic()+
  ggtitle("Graph of percent duplicates for R1 trimmed")+ 
  theme(axis.text.x=element_text(vjust = .2,angle=90))+
  scale_y_continuous( limits = c(0,100),expand = expansion(mult = c(0, .1)))
```

```{r dup info 4, fig.width = 14}
combo_trim_df %>% 
  dplyr::filter(read=="R2") %>% 
  ggplot(., aes(x = Sample, y= `FastQC_mqc-generalstats-fastqc-percent_duplicates`))+
  geom_col(aes(fill=Histone_Mark)) +
  theme_classic()+
  ggtitle("Graph of percent duplicates for R2 trimmed")+ 
  theme(axis.text.x=element_text(vjust = .2,angle=90))+
  scale_y_continuous(limits = c(0,100), expand = expansion(mult = c(0, .1)))
```

### Alignment Analysis

#### Data Initialization
```{r data initialization}
alignResult = c()
for(sample in sampleinfo$`Library ID`){
  alignRes = read.table(paste0("data/sams/", sample, ".log"), header = FALSE, fill = TRUE)
  alignRate = substr(alignRes$V1[6], 1, nchar(as.character(alignRes$V1[6]))-1)
  alignResult = data.frame(ID = sample, 
                           Paired_Reads = alignRes$V1[1] %>% as.character %>% as.numeric, 
                           aligned_concordant_0 = alignRes$V1[3] %>% as.character %>% as.numeric,
                           aligned_concordant_1 = alignRes$V1[4] %>% as.character %>% as.numeric,
                           aligned_concordant_g1 = alignRes$V1[5] %>% as.character %>% as.numeric,
                           MappedFragNum_hg38 = alignRes$V1[4] %>% as.character %>% as.numeric + alignRes$V1[5] %>% as.character %>% as.numeric, 
                           percent_alignment = alignRate %>% as.numeric)  %>% rbind(alignResult, .)
}
alignResult %>% mutate(percent_alignment = paste0(percent_alignment, "%"))

for_plots <- alignResult %>% 
  left_join(.,sampleinfo, by=c("ID"="Library ID"))%>% 
  dplyr::select(ID:aligned_concordant_0,aligned_concordant_1, aligned_concordant_g1,percent_alignment, Histone_Mark, Individual, Treatment, Timepoint) %>% 
  distinct()
```

#### Read Visualization
```{r align vis 1, fig.width = 14}
for_plots %>% 
  group_by(Histone_Mark) %>% 
  ggplot(., aes(x=ID, y=Paired_Reads))+
    geom_col(aes(fill = Histone_Mark)) +
  theme_classic()+
  ggtitle("Graph of total paired reads")+ 
  theme(axis.text.x=element_text(vjust = .2,angle=90))+
  scale_y_continuous( expand = expansion(mult = c(0, .1)))
```

```{r align vis 2, fig.width = 14}
for_plots %>% 
  group_by(Histone_Mark) %>% 
  ggplot(., aes(x=ID, y=percent_alignment))+
    geom_col(aes(fill = Histone_Mark)) +
  theme_classic()+
  ggtitle("Percent aligned of paired reads") + 
  theme(axis.text.x=element_text(vjust = .2,angle=90))+
  scale_y_continuous(expand = expansion(mult = c(0, .1)))+
  coord_cartesian(ylim=c(80,100))
```

```{r align vis 3, fig.width = 14}
for_plots %>% 
  group_by(Histone_Mark) %>% 
   mutate(percent_aligned_unique = round(aligned_concordant_1 / Paired_Reads * 100, 2)) %>% 
  ggplot(., aes(x=ID, y=percent_aligned_unique))+
    geom_col(aes(fill = Histone_Mark)) +
  theme_classic()+
  ggtitle("Percentage of paired reads aligning once")+ 
  theme(axis.text.x=element_text(vjust = .2,angle=90))+
  scale_y_continuous( expand = expansion(mult = c(0, .1)))
```

### Read Analysis

#### Data Initialization
```{r read data}
file_list_filter <- list.files(path="data/bam_no_multi",
           pattern ="frag_len_count\\.txt$",full.names = TRUE)
read_and_label <- function(file) {
  df <- read_delim(file, delim = "\t", col_names = c("Col1", "Col2"))  # Adjust delimiter if needed
  df <- df %>%
    mutate(File = basename(file),  # Add filename column
  weight = Col2/sum(Col2))
  return(df)
}
combined_df <- map_df(file_list_filter, read_and_label)

annotated_combo_df <- combined_df %>% 
  mutate(sample = gsub("_frag_len_count.txt","",File)) %>% 
  left_join(., sampleinfo, by = c("sample"="Library ID"))
```

#### Read Visualization
```{r read vis 1, fig.width = 14}
annotated_combo_df %>% 
  dplyr::filter(Histone_Mark=="H3K9me3") %>% 
  ggplot(., aes(x=Col1, y=Col2, color = sample))+
  geom_line(size=1)+
  scale_x_continuous(breaks = seq(0, max(annotated_combo_df$Col1), by = 50))+
   facet_wrap(~sample)+
  labs(title = "Fragment length, H3K9me3",
       x = "Fragment Length (bp)",
       y = "Count",
       color= "Sample")+
  theme_minimal()
```

```{r read vis 2, fig.width = 14}
annotated_combo_df %>% 
  dplyr::filter(Histone_Mark=="H3K9me3") %>%
  ggplot(., aes(x=sample, y=Col1, weight = weight,fill = Histone_Mark))+
geom_violin(bw = 5) +
    scale_y_continuous(breaks = seq(0, 800, 50)) +
   theme_bw(base_size = 20) +
    ggpubr::rotate_x_text(angle = 90) +
  ggtitle("Fragment lengths for H3K9me3")+
    ylab("Fragment Length") +
    xlab("")
```

```{r read vis 3, fig.width = 14}
annotated_combo_df %>% 
  dplyr::filter(Histone_Mark=="H3K27ac") %>% 
  ggplot(., aes(x=Col1, y=Col2, color = sample))+
  geom_line(size=1)+
  scale_x_continuous(breaks = seq(0, max(annotated_combo_df$Col1), by = 50))+
   facet_wrap(~sample)+
  labs(title = "Fragment length, H3K27ac",
       x = "Fragment Length (bp)",
       y = "Count",
       color= "Sample")+
  theme_minimal()
```

```{r read vis 4, fig.width = 14}
annotated_combo_df %>% 
  dplyr::filter(Histone_Mark=="H3K27ac") %>%
  ggplot(., aes(x=sample, y=Col1, weight = weight,fill = Histone_Mark))+
geom_violin(bw = 5) +
    scale_y_continuous(breaks = seq(0, 800, 50)) +
   theme_bw(base_size = 20) +
    ggpubr::rotate_x_text(angle = 90) +
  ggtitle("Fragment lengths for H3K27ac")+
    ylab("Fragment Length") +
    xlab("")
```

```{r read vis 5, fig.width = 14}
annotated_combo_df %>% 
  dplyr::filter(Histone_Mark=="H3K27me3") %>% 
  ggplot(., aes(x=Col1, y=Col2, color = sample))+
  geom_line(size=1)+
  scale_x_continuous(breaks = seq(0, max(annotated_combo_df$Col1), by = 50))+
   facet_wrap(~sample)+
  labs(title = "Fragment length, H3K27me3",
       x = "Fragment Length (bp)",
       y = "Count",
       color= "Sample")+
  theme_minimal()
```

```{r read vis 6, fig.width = 14}
annotated_combo_df %>% 
  dplyr::filter(Histone_Mark=="H3K27me3") %>%
  ggplot(., aes(x=sample, y=Col1, weight = weight,fill = Histone_Mark))+
geom_violin(bw = 5) +
    scale_y_continuous(breaks = seq(0, 800, 50)) +
   theme_bw(base_size = 20) +
    ggpubr::rotate_x_text(angle = 90) +
  ggtitle("Fragment lengths for H3K27me3")+
    ylab("Fragment Length") +
    xlab("")
```

```{r read vis 7, fig.width = 14}
annotated_combo_df %>% 
  dplyr::filter(Histone_Mark=="H3K36me3") %>% 
  ggplot(., aes(x=Col1, y=Col2, color = sample))+
  geom_line(size=1)+
  scale_x_continuous(breaks = seq(0, max(annotated_combo_df$Col1), by = 50))+
   facet_wrap(~sample)+
  labs(title = "Fragment length, H3K36me3",
       x = "Fragment Length (bp)",
       y = "Count",
       color= "Sample")+
  theme_minimal()
```

```{r read vis 8, fig.width = 14}
annotated_combo_df %>% 
  dplyr::filter(Histone_Mark=="H3K36me3") %>%
  ggplot(., aes(x=sample, y=Col1, weight = weight,fill = Histone_Mark))+
geom_violin(bw = 5) +
    scale_y_continuous(breaks = seq(0, 800, 50)) +
   theme_bw(base_size = 20) +
    ggpubr::rotate_x_text(angle = 90) +
  ggtitle("Fragment lengths for H3K36me3")+
    ylab("Fragment Length") +
    xlab("")
```

#### Tagging Questionable Libraries by Frag Len
```{r frag tag}
peaks <- data.frame(sample = unique(annotated_combo_df$sample))
peaks[,"peakNum"] <- NA
for (s in peaks$sample) {
  weights <- annotated_combo_df %>%
    dplyr::filter(sample==s) %>%
    dplyr::select(Col1, weight)
  weights$smooth <- smooth_data(x = weights$Col1, y = weights$weight, sm_method = "moving-average", window_width_n = 15)
  weights$peak <-find_peaks(weights$smooth, span = 31, ignore_threshold = 0.01)
  peaks[peaks$sample == s,"peakNum"] <- sum(as.numeric(weights$peak[-1:-150]))
}
questionable_frag = peaks[(peaks$peakNum == 0),]
questionable_frag %>%
  left_join(., sampleinfo, by =c("sample"="Library ID"))
```

### Read Analysisafter Filtering

#### Data Initialization
```{r read noM data}
file_list_noM <- list.files(path="data/bam_final",
           pattern ="frag_len_noM\\.txt$",full.names = TRUE)
read_and_label <- function(file) {
  df <- read_delim(file, delim = "\t", col_names = c("Col1", "Col2"))  # Adjust delimiter if needed
  df <- df %>%
    mutate(File = basename(file),  # Add filename column
  weight = Col2/sum(Col2))
  return(df)
}
combined_df <- map_df(file_list_noM, read_and_label)

annotated_noM_df <- combined_df %>% 
  mutate(sample = gsub("_frag_len_noM.txt","",File)) %>% 
  left_join(., sampleinfo, by = c("sample"="Library ID"))
```

#### Read Visualization
```{r read noM vis 1, fig.width = 14}
annotated_noM_df %>% 
  dplyr::filter(Histone_Mark=="H3K9me3") %>% 
  ggplot(., aes(x=Col1, y=Col2, color = sample))+
  geom_line(size=1)+
  scale_x_continuous(breaks = seq(0, max(annotated_combo_df$Col1), by = 50))+
   facet_wrap(~sample)+
  labs(title = "Fragment length, H3K9me3",
       x = "Fragment Length (bp)",
       y = "Count",
       color= "Sample")+
  theme_minimal()
```

```{r read noM vis 2, fig.width = 14}
annotated_noM_df %>% 
  dplyr::filter(Histone_Mark=="H3K9me3") %>%
  ggplot(., aes(x=sample, y=Col1, weight = weight,fill = Histone_Mark))+
geom_violin(bw = 5) +
    scale_y_continuous(breaks = seq(0, 800, 50)) +
   theme_bw(base_size = 20) +
    ggpubr::rotate_x_text(angle = 90) +
  ggtitle("Fragment lengths for H3K9me3")+
    ylab("Fragment Length") +
    xlab("")
```

```{r read noM vis 3, fig.width = 14}
annotated_noM_df %>% 
  dplyr::filter(Histone_Mark=="H3K27ac") %>% 
  ggplot(., aes(x=Col1, y=Col2, color = sample))+
  geom_line(size=1)+
  scale_x_continuous(breaks = seq(0, max(annotated_combo_df$Col1), by = 50))+
   facet_wrap(~sample)+
  labs(title = "Fragment length, H3K27ac",
       x = "Fragment Length (bp)",
       y = "Count",
       color= "Sample")+
  theme_minimal()
```

```{r read noM vis 4, fig.width = 14}
annotated_noM_df %>% 
  dplyr::filter(Histone_Mark=="H3K27ac") %>%
  ggplot(., aes(x=sample, y=Col1, weight = weight,fill = Histone_Mark))+
geom_violin(bw = 5) +
    scale_y_continuous(breaks = seq(0, 800, 50)) +
   theme_bw(base_size = 20) +
    ggpubr::rotate_x_text(angle = 90) +
  ggtitle("Fragment lengths for H3K27ac")+
    ylab("Fragment Length") +
    xlab("")
```

```{r read noM vis 5, fig.width = 14}
annotated_noM_df %>% 
  dplyr::filter(Histone_Mark=="H3K27me3") %>% 
  ggplot(., aes(x=Col1, y=Col2, color = sample))+
  geom_line(size=1)+
  scale_x_continuous(breaks = seq(0, max(annotated_combo_df$Col1), by = 50))+
   facet_wrap(~sample)+
  labs(title = "Fragment length, H3K27me3",
       x = "Fragment Length (bp)",
       y = "Count",
       color= "Sample")+
  theme_minimal()
```

```{r read noM vis 6, fig.width = 14}
annotated_noM_df %>% 
  dplyr::filter(Histone_Mark=="H3K27me3") %>%
  ggplot(., aes(x=sample, y=Col1, weight = weight,fill = Histone_Mark))+
geom_violin(bw = 5) +
    scale_y_continuous(breaks = seq(0, 800, 50)) +
   theme_bw(base_size = 20) +
    ggpubr::rotate_x_text(angle = 90) +
  ggtitle("Fragment lengths for H3K27me3")+
    ylab("Fragment Length") +
    xlab("")
```

```{r read noM vis 7, fig.width = 14}
annotated_noM_df %>% 
  dplyr::filter(Histone_Mark=="H3K36me3") %>% 
  ggplot(., aes(x=Col1, y=Col2, color = sample))+
  geom_line(size=1)+
  scale_x_continuous(breaks = seq(0, max(annotated_combo_df$Col1), by = 50))+
   facet_wrap(~sample)+
  labs(title = "Fragment length, H3K36me3",
       x = "Fragment Length (bp)",
       y = "Count",
       color= "Sample")+
  theme_minimal()
```

```{r read noM vis 8, fig.width = 14}
annotated_noM_df %>% 
  dplyr::filter(Histone_Mark=="H3K36me3") %>%
  ggplot(., aes(x=sample, y=Col1, weight = weight,fill = Histone_Mark))+
geom_violin(bw = 5) +
    scale_y_continuous(breaks = seq(0, 800, 50)) +
   theme_bw(base_size = 20) +
    ggpubr::rotate_x_text(angle = 90) +
  ggtitle("Fragment lengths for H3K36me3")+
    ylab("Fragment Length") +
    xlab("")
```

#### Tagging Questionable Libraries by Frag Len
```{r frag tag after filter}
peaks <- data.frame(sample = unique(annotated_noM_df$sample))
peaks[,"peakNum"] <- NA
for (s in peaks$sample) {
  weights <- annotated_combo_df %>%
    dplyr::filter(sample==s) %>%
    dplyr::select(Col1, weight)
  weights$smooth <- smooth_data(x = weights$Col1, y = weights$weight, sm_method = "moving-average", window_width_n = 15)
  weights$peak <-find_peaks(weights$smooth, span = 31, ignore_threshold = 0.01)
  peaks[peaks$sample == s,"peakNum"] <- sum(as.numeric(weights$peak[-1:-150]))
}
questionable_frag_filter = peaks[(peaks$peakNum == 0),]
questionable_frag_filter %>%
  left_join(., sampleinfo, by =c("sample"="Library ID"))
```

### Peak Calling
