---
title: "Peak Analysis"
author: "Steven Yu"
date: "2025-07-14"
output: workflowr::wflow_html
editor_options:
  chunk_output_type: inline
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
	echo = TRUE,
	message = FALSE,
	warning = FALSE,
	dev = c("png","pdf")
)
```

## Peak Anaylsis

#### Loading Packages 
```{r load packages}
library(tidyverse)
library(readr)
library(edgeR)
library(ComplexHeatmap)
library(data.table)
library(dplyr)
library(stringr)
library(ggplot2)
library(viridis)
library(DT)
library(kableExtra)
library(genomation)
library(GenomicRanges)
library(chromVAR) ## For FRiP analysis and differential analysis
library(DESeq2) ## For differential analysis section
library(ggpubr) ## For customizing figures
library(corrplot) ## For correlation plot
library(ggpmisc)
library(gcplyr)
```

#### Data Initialization
```{r init}
sampleinfo <- read_delim("data/sample_info.tsv", delim = "\t")
multiqc_gene_stats_trim <- read_delim("data/multiqc_data_trim/multiqc_general_stats.txt",delim = "\t")
multiqc_fastqc_trim <- read_delim("data/multiqc_data_trim/multiqc_fastqc.txt",delim = "\t")
```

#### Functions
```{r functions}
drug_pal <- c("#8B006D","#DF707E","#F1B72B", "#3386DD","#707031","#41B333")
pca_plot <-
  function(df,
           col_var = NULL,
           shape_var = NULL,
           title = "") {
    ggplot(df) + geom_point(aes_string(
      x = "PC1",
      y = "PC2",
      color = col_var,
      shape = shape_var
    ),
    size = 5) +
      labs(title = title, x = "PC 1", y = "PC 2") +
      scale_color_manual(values = c(
        "#8B006D",
        "#DF707E",
        "#F1B72B",
        "#3386DD",
        "#707031",
        "#41B333"
      ))
  }
pca_var_plot <- function(pca) {
  # x: class == prcomp
  pca.var <- pca$sdev ^ 2
  pca.prop <- pca.var / sum(pca.var)
  var.plot <-
    qplot(PC, prop, data = data.frame(PC = 1:length(pca.prop),
                                      prop = pca.prop)) +
    labs(title = 'Variance contributed by each PC',
         x = 'PC', y = 'Proportion of variance')
  plot(var.plot)
}

calc_pca <- function(x) {
  # Performs principal components analysis with prcomp
  # x: a sample-by-gene numeric matrix
  prcomp(x, scale. = TRUE, retx = TRUE)
}

get_regr_pval <- function(mod) {
  # Returns the p-value for the Fstatistic of a linear model
  # mod: class lm
  stopifnot(class(mod) == "lm")
  fstat <- summary(mod)$fstatistic
  pval <- 1 - pf(fstat[1], fstat[2], fstat[3])
  return(pval)
}

plot_versus_pc <- function(df, pc_num, fac) {
  # df: data.frame
  # pc_num: numeric, specific PC for plotting
  # fac: column name of df for plotting against PC
  pc_char <- paste0("PC", pc_num)
  # Calculate F-statistic p-value for linear model
  pval <- get_regr_pval(lm(df[, pc_char] ~ df[, fac]))
  if (is.numeric(df[, f])) {
    ggplot(df, aes_string(x = f, y = pc_char)) + geom_point() +
      geom_smooth(method = "lm") + labs(title = sprintf("p-val: %.2f", pval))
  } else {
    ggplot(df, aes_string(x = f, y = pc_char)) + geom_boxplot() +
      labs(title = sprintf("p-val: %.2f", pval))
  }
}
x_axis_labels = function(labels, every_nth = 1, ...) {
  axis(side = 1,
       at = seq_along(labels),
       labels = F)
  text(
    x = (seq_along(labels))[seq_len(every_nth) == 1],
    y = par("usr")[3] - 0.075 * (par("usr")[4] - par("usr")[3]),
    labels = labels[seq_len(every_nth) == 1],
    xpd = TRUE,
    ...
  )
}
```

### Peak Calling MACS 2

#### Data Initialization
```{r peak data}
peak_ct <- read_delim("data/peaks/peaks_cts.tsv", delim = "\t")
H3K27ac_peaks <- read_delim("data/peaks/H3K27ac_macs2_nolambda_1e5_results.tsv",delim = "\t")
H3K27ac_peaks_noModel <- read_delim("data/peaks/H3K27ac_macs2_noModel_nolambda_1e5_results.tsv",delim = "\t")
H3K27me3_peaks <- read_delim("data/peaks/H3K27me3_macs2_broad_results.tsv",delim = "\t")
H3K36me3_peaks <- read_delim("data/peaks/H3K36me3_macs2_broad_results.tsv",delim = "\t")
H3K9me3_peaks <- read_delim("data/peaks/H3K9me3_macs2_nolambda_1e5_results.tsv",delim = "\t")
H3K9me3_peaks_noModel <- read_delim("data/peaks/H3K9me3_macs2_noModel_nolambda_1e5_results.tsv",delim = "\t")

all_peak <- rbind(H3K27ac_peaks, H3K27me3_peaks, H3K36me3_peaks, H3K9me3_peaks)
all_peak_noModel <- rbind(H3K27ac_peaks_noModel, H3K27me3_peaks, H3K36me3_peaks, H3K9me3_peaks_noModel)

all_peak <- all_peak %>%
  dplyr::select(Sample, Total_Reads, Fragments, Reads_in_Peaks, FRiP) %>%
  left_join(.,sampleinfo, by=c("Sample"="Library ID")) %>%
  left_join(.,peak_ct, by=c("Sample"="Sample"))
all_peak <- all_peak[(!all_peak$Treatment %in% "5FU"),]
all_peak_noModel <- all_peak %>%
  dplyr::select(Sample, Total_Reads, Fragments, Reads_in_Peaks, FRiP) %>%
  left_join(.,sampleinfo, by=c("Sample"="Library ID")) %>%
  left_join(.,peak_ct, by=c("Sample"="Sample"))
all_peak_noModel <- all_peak_noModel[(!all_peak_noModel$Treatment %in% "5FU"),]
```

#### Peak Visualization
```{r peak ct, fig.width=14}
all_peak %>% 
   ggplot(.,aes(x=Sample, y=Count,fill=Histone_Mark))+
   geom_col()+
   ylab("Count")+
   theme_classic()+
  # facet_wrap(~histone)+
  ggtitle("Peak number for all samples")+ 
  theme(axis.text.x=element_text(vjust = .2,angle=90))+
  scale_y_continuous( expand = expansion(mult = c(0, .1)))
```

```{r peak ct box}
all_peak %>% 
  ggplot(., aes (x=Histone_Mark, y = Count, fill = Histone_Mark))+
  geom_boxplot()+
   ylab("Count")+
   theme_classic()+
  # facet_wrap(~histone)+
  ggtitle("Peak count across histones")
```

```{r peak ct grouptx}
all_peak %>% 
  ggplot(., aes (x=Treatment, y = Count, fill = Histone_Mark))+
  geom_boxplot()+
   ylab("Count")+
   theme_classic()+
  # facet_wrap(~histone)+
  ggtitle("Peak count across histones")
```

```{r peak ct grouptime}
all_peak %>% 
  ggplot(., aes (x=Timepoint, y = Count, fill = Histone_Mark))+
  geom_boxplot()+
   ylab("Count")+
   theme_classic()+
  # facet_wrap(~histone)+
  ggtitle("Peak count across histones")
```

#### Tagging Questionable Libraries by FRiP
```{r frip tag}
questionable_frip = all_peak[(all_peak$FRiP < 0.02),]
questionable_frip
```

```{r frip tag noModel}
questionable_frip_noModel = all_peak_noModel[(all_peak_noModel$FRiP < 0.02),]
questionable_frip_noModel
```

#### Renaming sample IDs
```{r rename}
all_peak <- all_peak %>%
  mutate(Sample=paste0(Individual,"_",Treatment,"_",Timepoint,"_",Histone_Mark))

all_peak_noModel <- all_peak_noModel %>%
  mutate(Sample=paste0(Individual,"_",Treatment,"_",Timepoint,"_",Histone_Mark))
```

### Peak Cut Off Analysis

#### Cut Off Analysis for H3K27ac
```{r peak cutoff H3K27ac 1, fig.width=14, fig.height=28}
H3K27ac <- sampleinfo %>%
  dplyr::filter(Histone_Mark=="H3K27ac")
cutoff <- data.frame(matrix(nrow = 0, ncol = 6))
colnames(cutoff) = c("Sample", "pscore", "qscore", "npeaks", "lpeaks", "avelpeak")
for (sample in H3K27ac$`Library ID`) {
  filename <- paste("data/peaks/H3K27ac/", sample, "_macs3_noModel_cutoff_analysis.txt", sep = "")
  temp <- read_delim(filename, delim = "\t")
  temp$Sample <- sample
  cutoff <- rbind(cutoff, temp)
}
H3K27ac <- left_join(H3K27ac, cutoff, by =c("Library ID"="Sample"))
H3K27ac %>%  
  ggplot(., aes(x=H3K27ac$qscore, y=H3K27ac$npeaks, color = 'Library ID'))+
  geom_line(size=1)+
  scale_x_continuous(breaks = seq(0, max(H3K27ac$qscore), by = 1))+
  facet_wrap(~`Library ID`, scales = "free", ncol = 5, switch = "y")+
  labs(title = "",
       x = "Q Score",
       y = "Peak Counts",
       color= "Sample")+
  theme_minimal()
```

```{r peak cutoff H3K27ac 2, fig.width=14, fig.height=28}
H3K27ac %>%  
  ggplot(., aes(x=H3K27ac$qscore, y=H3K27ac$lpeaks, color = 'Library ID'))+
  geom_line(size=1)+
  scale_x_continuous(breaks = seq(0, max(H3K27ac$qscore), by = 1))+
  facet_wrap(~`Library ID`, scales = "free", ncol = 5, switch = "y")+
  labs(title = "",
       x = "Q Score",
       y = "Total Peak Lengthss",
       color= "Sample")+
  theme_minimal()
```

```{r peak cutoff H3K27ac 3, fig.width=14, fig.height=28}
H3K27ac %>%  
  ggplot(., aes(x=H3K27ac$qscore, y=H3K27ac$avelpeak, color = 'Library ID'))+
  geom_line(size=1)+
  scale_x_continuous(breaks = seq(0, max(H3K27ac$qscore), by = 1))+
  facet_wrap(~`Library ID`, scales = "free", ncol = 5, switch = "y")+
  labs(title = "",
       x = "Q Score",
       y = "Average Peak Lengthss",
       color= "Sample")+
  theme_minimal()
```

#### Cut Off Analysis for H3K27me3
```{r peak cutoff H3K27me3 1, fig.width=14, fig.height=28}
H3K27me3 <- sampleinfo %>%
  dplyr::filter(Histone_Mark=="H3K27me3")
cutoff <- data.frame(matrix(nrow = 0, ncol = 6))
colnames(cutoff) = c("Sample", "pscore", "qscore", "npeaks", "lpeaks", "avelpeak")
for (sample in H3K27me3$`Library ID`) {
  filename <- paste("data/peaks/H3K27me3/", sample, "_macs3_cutoff_analysis.txt", sep = "")
  temp <- read_delim(filename, delim = "\t")
  temp$Sample <- sample
  cutoff <- rbind(cutoff, temp)
}
H3K27me3 <- left_join(H3K27me3, cutoff, by =c("Library ID"="Sample"))

H3K27me3 <- H3K27me3[(H3K27me3$pscore >= 0.6),]

H3K27me3 %>%  
  ggplot(., aes(x=H3K27me3$qscore, y=H3K27me3$npeaks, color = 'Library ID'))+
  geom_line(size=1)+
  # geom_point(size=2,alpha =0.7)+
  scale_x_continuous(breaks = seq(0.6, max(H3K27me3$qscore), by = 0.6))+
  facet_wrap(~`Library ID`, scales = "free", ncol = 5, switch = "y")+
  labs(title = "",
       x = "Q Score",
       y = "Peak Counts",
       color= "Sample")+
  theme_minimal()
```

```{r peak cutoff H3K27me3 2, fig.width=14, fig.height=28}
H3K27me3 %>%  
  ggplot(., aes(x=H3K27me3$qscore, y=H3K27me3$lpeaks, color = 'Library ID'))+
  geom_line(size=1)+
  scale_x_continuous(breaks = seq(0.6, max(H3K27me3$qscore), by = 0.6))+
  facet_wrap(~`Library ID`, scales = "free", ncol = 5, switch = "y")+
  labs(title = "",
       x = "Q Score",
       y = "Total Peak Lengths",
       color= "Sample")+
  theme_minimal()
```

```{r peak cutoff H3K27me3 3, fig.width=14, fig.height=28}
H3K27me3 %>%  
  ggplot(., aes(x=H3K27me3$qscore, y=H3K27me3$avelpeak, color = 'Library ID'))+
  geom_line(size=1)+
  scale_x_continuous(breaks = seq(0.6, max(H3K27me3$qscore), by = 0.6))+
  facet_wrap(~`Library ID`, scales = "free", ncol = 5, switch = "y")+
  labs(title = "",
       x = "Q Score",
       y = "Average Peak Lengths",
       color= "Sample")+
  theme_minimal()
```

#### Cut Off Analysis for H3K36me3
```{r peak cutoff H3K36me3 1, fig.width=14, fig.height=28}
H3K36me3 <- sampleinfo %>%
  dplyr::filter(Histone_Mark=="H3K36me3")
cutoff <- data.frame(matrix(nrow = 0, ncol = 6))
colnames(cutoff) = c("Sample", "pscore", "qscore", "npeaks", "lpeaks", "avelpeak")
for (sample in H3K36me3$`Library ID`) {
  filename = paste("data/peaks/H3K36me3/", sample, "_macs3_cutoff_analysis.txt", sep = "")
  temp <- read_delim(filename, delim = "\t")
  temp$Sample <- sample
  cutoff <- rbind(cutoff, temp)
}
H3K36me3 <- left_join(H3K36me3, cutoff, by =c("Library ID"="Sample"))

H3K36me3 <- H3K36me3[(H3K36me3$pscore >= 0.6),]

H3K36me3 %>%  
  ggplot(., aes(x=H3K36me3$qscore, y=H3K36me3$npeaks, color = 'Library ID'))+
  geom_line(size=1)+
  # geom_point(size=2,alpha =0.7)+
  scale_x_continuous(breaks = seq(0.6, max(H3K36me3$qscore), by = 0.6))+
  facet_wrap(~`Library ID`, scales = "free", ncol = 5, switch = "y")+
  labs(title = "",
       x = "Q Score",
       y = "Peak Counts",
       color= "Sample")+
  theme_minimal()
```

```{r peak cutoff H3K36me3 2, fig.width=14, fig.height=28}
H3K36me3 %>%  
  ggplot(., aes(x=H3K36me3$qscore, y=H3K36me3$lpeaks, color = 'Library ID'))+
  geom_line(size=1)+
  scale_x_continuous(breaks = seq(0.6, max(H3K36me3$qscore), by = 0.6))+
  facet_wrap(~`Library ID`, scales = "free", ncol = 5, switch = "y")+
  labs(title = "",
       x = "Q Score",
       y = "Total Peak Lengths",
       color= "Sample")+
  theme_minimal()
```

```{r peak cutoff H3K36me3 3, fig.width=14, fig.height=28}
H3K36me3 %>%  
  ggplot(., aes(x=H3K36me3$qscore, y=H3K36me3$avelpeak, color = 'Library ID'))+
  geom_line(size=1)+
  scale_x_continuous(breaks = seq(0.6, max(H3K36me3$qscore), by =0.6))+
  facet_wrap(~`Library ID`, scales = "free", ncol = 5, switch = "y")+
  labs(title = "",
       x = "Q Score",
       y = "Average Peak Lengths",
       color= "Sample")+
  theme_minimal()
```

#### Cut Off Analysis for H3K9me3
```{r peak cutoff H3K9me3 1, fig.width=14, fig.height=28}
H3K9me3 <- sampleinfo %>%
  dplyr::filter(Histone_Mark=="H3K9me3")
cutoff <- data.frame(matrix(nrow = 0, ncol = 6))
colnames(cutoff) = c("Sample", "pscore", "qscore", "npeaks", "lpeaks", "avelpeak")
for (sample in H3K9me3$`Library ID`) {
  filename = paste("data/peaks/H3K9me3/", sample, "_macs3_noModel_cutoff_analysis.txt", sep = "")
  temp <- read_delim(filename, delim = "\t")
  temp$Sample <- sample
  cutoff <- rbind(cutoff, temp)
}
H3K9me3 <- left_join(H3K9me3, cutoff, by =c("Library ID"="Sample"))

H3K9me3 %>%  
  ggplot(., aes(x=H3K9me3$qscore, y=H3K9me3$npeaks, color = 'Library ID'))+
  geom_line(size=1)+
  # geom_point(size=2,alpha =0.7)+
  scale_x_continuous(breaks = seq(0, max(H3K9me3$qscore), by = 1))+
  facet_wrap(~`Library ID`, scales = "free", ncol = 5, switch = "y")+
  labs(title = "",
       x = "Q Score",
       y = "Peak Counts",
       color= "Sample")+
  theme_minimal()
```

```{r peak cutoff H3K9me3 2, fig.width=14, fig.height=28}
H3K9me3 %>%  
  ggplot(., aes(x=H3K9me3$qscore, y=H3K9me3$lpeaks, color = 'Library ID'))+
  geom_line(size=1)+
  scale_x_continuous(breaks = seq(0, max(H3K9me3$qscore), by = 1))+
  facet_wrap(~`Library ID`, scales = "free", ncol = 5, switch = "y")+
  labs(title = "",
       x = "Q Score",
       y = "Total Peak Lengths",
       color= "Sample")+
  theme_minimal()
```

```{r peak cutoff H3K9me3 3, fig.width=14, fig.width=28}
H3K9me3 %>%  
  ggplot(., aes(x=H3K9me3$qscore, y=H3K9me3$avelpeak, color = 'Library ID'))+
  geom_line(size=1)+
  scale_x_continuous(breaks = seq(0, max(H3K9me3$qscore), by = 1))+
  facet_wrap(~`Library ID`, scales = "free", ncol = 5, switch = "y")+
  labs(title = "",
       x = "Q Score",
       y = "Average Peak Lengths",
       color= "Sample")+
  theme_minimal()
```

### H3K27ac Count Analysis
```{r H3K27ac HeatMap 1}
#H3K27ac_peaks <- all_peak %>% 
#  dplyr::filter(Histone_Mark=="H3K27ac") %>%
#  dplyr::select()
#  cpm(., log = TRUE) %>% 
#  cor()

#H3K27ac_peaks_noModel <- all_peak_noModel %>% 
#  dplyr::filter(Histone_Mark=="H3K27ac") %>%
#  cpm(., log = TRUE) %>% 
#  cor()
# Waiting on Peak cutoff analysis and Feature Counts
```
### H3K27me3 Count Analysis

### H3K36me3 Count Analysis

### H3K9me3 Count Analysis

### Peak Calling MACS 3


